\subsection{Extra-functional requirements}



\subsubsection{Performance requirements }


\begin{itemize}
\item System shall perform real time operations within the constraints of the host hardware and network system. 
\item Imported libraries shall not hinder performance beyond a negligible amount
\item Graphics processing shall not hinder performance beyond a reasonable amount
\item Target latency should be near 10 milliseconds

\hfill \initBox
\end{itemize}
 
\subsubsection{Reliability requirements}
\begin{itemize}
\item System shall provide proper handling of packet loss and/or loss of connectivity
\item System should provide meaningful indicators to the user when there is loss of connectivity and/or packet loss
\item System shall have methods to ensure reasonably quick restart after crashing
\begin{itemize}
\item After such a crash, system shall restart to the last good state
\end{itemize}
\end{itemize}

\hfill \initBox

\subsubsection{Security}
\begin{itemize}
\item Since RV3K is a one-way, standalone system, security is up to the discretion of users, and the parties who stream content to public or private networks.
\item RV3K shall be easily modifiable in such a way that it could support end-to-end encryption, or other security enhancements, but this will not be a feature of version \version.
\end{itemize}
\medskip

\hfill \initBox

\subsubsection{Usability requirements}
\begin{itemize}
\item The RV3K UI should be intuitive and easy to understand. Every pixel should have a purpose.
\item User controls and settings should function responsively and be clearly labeled.
\item User interface documentation should be easily invoked and/or accessible to the user.
\end{itemize}
\medskip

\hfill \initBox

\paragraph{Accessibility}
\begin{itemize}
\item Accessibility features will not be required, however, UI design should consider visual coherence, and use alt-tags whenever possible.
\item Color schemes shall not be confusing to persons with color deficient vision.
\end{itemize}
\medskip

\hfill \initBox

\subsubsection{Maintainability}
Code shall be well commented, well structured, and easy for an undergrad CS student to work on and understand.

\begin{itemize}
\item No magic: code shall maintain readability by avoiding convoluted or overly-clever blocks

\item Code should follow best practices for whichever languages and frameworks are used

\item Code should avoid obscure and/or overly complicated languages and frameworks
\end{itemize}
\medskip

\hfill \initBox
\subsubsection{Licensing requirements}


Licensing requirements are covered in the license agreement document and copyright
notice at the beginning of this document.

\hfill \initBox
