\section{User interface}
The user interface is modularized by an Angular.js framework


\subsection{Web-app layout}
Layout is configured using CSS, and angular material directives as described in index.html

\subsection{User interaction and controls}
User interaction is limited to a few buttons in the navbar section of the app.



\subsection{Real-time data visualization elements}
  The design of the user interface includes 5 separate elements:
  \subsubsection{Live streaming video of the rocket launch}
    This element is a video player that displays live video of the rocket launch.
  \subsubsection{An 'earth frame view' element}
    This element is a map view of the rocket position in relation to the surface
	of the earth.
  \subsubsection{An 'attitude' element}
    This element is a view of the rocket showing the rocket orientation.
  \subsubsection{A telemetry data element}
    This element is a visualization of numerical telemetry data including graphs
	and charts.
  \subsubsection{An 'at a glance' element}
    This element is a comprehensive numerical view of the rocket telemetry data.

\subsection{Visual design considerations}
  The visual design of the user interface facilitates a comprehensive and
  visually stimulating rocket launch viewing experience that caters to the
  individual's viewing preferences. The design allows for the expansion of
  each visual element so that it is the center of the web page in order for the
  user to be able to clearly view each element. The user is able to switch
  which element is highlighted at the click of a button so that he/she is able
  concentrate on the desired element. The design also allows the user to view
  a data intensive display that encompasses all of the telemetry data being recorded
  from the rocket during the launch to track the important numerical data important
  in a rocket launch. As the user changes the visual layout through the navigation
  controls, the animations are smooth and easy to follow.
